Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-02-29 main_paper.tex
Minor word change in the introduction
There are settings where positions above or below the cutoff are related
to the other factors affecting outcomes. We want to make sure that we're
not claiming RD always works, only that it works when that assumption
is plausible.

\newpage
\section{Introduction}
Regression Discontinuity (RD) designs have emerged in the last decade as an
important and popular research design strategy for analyzing the causal impact
of policies and interventions in several fields of the social sciences,
including economics, political science, public policy, and sociology.
This research strategy exploits the fact that many programs use somewhat
arbitrary thresholds to determine whether or not to provide a ``treatment,''
usually relying on some type of score, which this literature calls a ``running
variable.'' In its basic version, the sharp RD,  individuals or groups with score above a
certain threshold receive treatment while the ones below that cutoff are left
untreated.
The identification of the treatment effect at the threshold is then based on
comparing treated and untreated units at the cutoff. Since being just above
or below the arbitrary cutoff is credibly not related to other factors impacting
outcomes, including their unobserved characteristics,  differences between 
treated and untreated individuals at the cutoff can be plausibly attributed to the
treatment alone. As a practical matter this involves comparing units within a
bandwidth just above and just below the threshold.

>>>>

\newpage
\section{Introduction}
Regression Discontinuity (RD) designs have emerged in the last decade as an
important and popular research design strategy for analyzing the causal impact
of policies and interventions in several fields of the social sciences,
including economics, political science, public policy, and sociology.
This research strategy exploits the fact that many programs use somewhat
arbitrary thresholds to determine whether or not to provide a ``treatment,''
usually relying on some type of score, which this literature calls a ``running
variable.'' In its basic version, the sharp RD,  individuals or groups with score above a
certain threshold receive treatment while the ones below that cutoff are left
untreated.
The identification of the treatment effect at the threshold is then based on
comparing treated and untreated units at the cutoff. When a subject's
position just above or below the cutoff is credibly not related to
other factors impacting outcomes, including their unobserved
characteristics, differences between treated and untreated individuals
at the cutoff can be plausibly attributed to the treatment alone. As a
practical matter this involves comparing units within a bandwidth just
above and just below the threshold.
